Security Audit of Safeplug

### 2014-01-24 report/results.tex
reorganize

\subsubsection{Internet Use}
\label{inetuse}
{\bf Setting up Safeplug.} The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configuration page.  The configuration page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

@@

{\bf Using the Internet.} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.

@@

{\bf Cookies.}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.  When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.  We experienced the same situation with Facebook and its corresponding ``like'' button.

>>>>

\subsection{Internet Use}
\label{inetuse}

\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configuration page.  The configuration page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

@@

\subsubsection{Using the Internet} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.

@@

\subsubsection{Cookies}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.  When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.  We experienced the same situation with Facebook and its corresponding ``like'' button.

### 2014-01-24 report/resultsSoftware.tex
reorganize

\subsubsection{Website Attack}
We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.  Setting this up is future work.

>>>>

\subsubsection{Website Attack}
It is also possible that an external website could perform this attack by returning a correctly formatted POST string.  This executes the same functionality as the Insider Attack, but the attacker does not require any knowledge of the Safeplug device -- specifically the IP address.  Any malicious Internet user with access to a web server can carry out this attack with less than 30 lines of Javascript code (See Appendix A).  The following steps are necessary for the attack to be successful:

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, including the POST request: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the  ranges.  
\item Tor is disabled.  It should be noted that the user must refresh her settings page to see the modified settings.  
\end{enumerate}

This exploits the RPC server in the same manner that the Insider Attack does.  While this attack requires a greater amount of time, the largest observed time to send requests to the 192.168.0.0/24 space was ~200 milliseconds; the entire attack costs ~400 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges.  In the case of a private network in the range of 10.0.0.0/16, the attack took ~12 minutes.  The 10.0.0.0/16 range is more commonly used for business networks, whereas the other ranges are more common in home networks; because Safeplug is geared towards home network use, we conclude that ~400 milliseconds is a reasonable amount of time for the attacker to spend.

In addition to disabling Tor, the attacker can modify any other settings on the device.  This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup].  It is also interesting to note that the source code for the configurations includes the ability to use the device as a Tor exit node; therefore, the attacker can enable/disable this functionality as long as the user has already set up the device as a Tor relay node.  Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.
